Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal distribution

### 2018-05-24 manuscript.tex
small text modif

While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\ref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM). The inclusion of the contrast parameter $A$ is justified by the expected behavior of the CCF in presence of active regions. Fig.~\ref{fig:spotA} shows that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width. This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
    \label{fig:spotA}
\end{figure*}
%

@@

In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$. The level for not rejecting the null hypothesis is fixed equal to $0.05$. The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV's of the star as caused by stellar activity.

@@

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Simulation Study} \label{sec:soap}
In order to evaluate the performance of the proposed SN approach for modelling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:faculae.correction}
\end{figure*}

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:spot.correction}
\end{figure*}

>>>>

While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\ref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM). The inclusion of the contrast parameter $A$ is justified by the fact that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
%   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width. This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
%    \label{fig:spotA}
%\end{figure*}
%%

@@

In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$. The level for not rejecting the null hypothesis is fixed equal to $0.05$. The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.

@@

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Simulation Study} \label{sec:soap}
In order to evaluate the performance of the proposed SN approach for modelling the CCF and the benefit of using the proposed correction for stellar activity (See Eq.~\ref{eq:RV:correction}), we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:faculae.correction}
\end{figure*}

@@

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:spot.correction}
\end{figure*}
